Supplementary information

### 2024-08-29 paper/supplementary_figures.Rmd
Cleaning targets pipeline (removing old code not used)

```{r dharma-lm, fig.cap="(ref:dharma-lm-cap)"}
knitr::include_graphics(here("report", "figures", "p_diagnotisc_model_fw_stab_comp.jpg"))
```

@@

@@

@@

```{r}
tar_read(tab_sem_simplified_eff) %>%
  kable(booktabs = TRUE,
    format = "latex",
    caption = "Standardised estimates from the supplementary Structural Equation
    Model which includes the partition of compensatory effects rising from
    environmental fluctuations and species interactions.",
    label = "sem-supp-coeff") %>%
collapse_rows(columns = 1, latex_hline = "major", valign = "middle") %>%
kable_styling(latex_options = c("striped", "hold_position"))
```

>>>>

@@

```{r}
met_cap <- "Examples of stochastic food-web simulations. a, Simulations with low
and high response diversity. b, simulations with low and high predator-prey mass
ratio (upper and bottom panels), low and high species richness (left and right
  panels). The food-webs are displayed on the side with the node size
being proportional to the average species biomass across the simulation. We
also display the food-web structure and the stability metrics. Across all
simulations, $h = 2$, $\\sigma_e = .3$. Low and high response diversity were
respectively $\\rho = 1$ and $\\rho = 0$. Low and high PPMR were respectively 1
and 100." %>%
str_replace_all("\\s+", " ")
```

```{r met, fig.cap = met_cap}
knitr::include_graphics(here("report", "figures", "p_methods.pdf"))
```

```{r dharma-lm, fig.cap="(ref:dharma-lm-cap)", out.width = "80%"}
knitr::include_graphics(here("report", "figures", "p_diagnotisc_model_fw_stab_comp.jpg"))
```

@@

```{r, eval = FALSE}
tar_read(tab_sem_simplified_eff) %>%
  kable(booktabs = TRUE,
    format = "latex",
    caption = "Standardised estimates from the supplementary Structural Equation
    Model which includes the partition of compensatory effects rising from
    environmental fluctuations and species interactions, and partition of
    statistical averaging effects (portfolio effects).", label =
    "sem-supp-coeff") %>%
  collapse_rows(columns = 1, latex_hline = "major", valign = "middle") %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

@@
